Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plots

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.7,
                 alpha = 1,
                 position = position_dodge(width = 4)) + 
    geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
                   size = 1.7,
                   alpha = 0.1,
                   position = position_dodge(width = 4)) +   
    geom_point(aes(shape = classification)) + 
  geom_line() + 
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

>>>>

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.7,
                 alpha = 1,
                 position = position_dodge(width = 4)) + 
    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
    #                size = 1.7,
    #                alpha = 0.1,
    #                position = position_dodge(width = 4)) +   
    geom_point(aes(shape = classification)) + 
  geom_line() + 
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}
